Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-03 docs/msr.tex
work in progress

First, we obtained a snapshot (January 2012) of the maven repository and
handled it locally to retreive a list of all the names of the artifacts that existed in the
repository.

>>>>

Initially, we obtained a snapshot (January 2012) of the maven repository and
handled it locally to retreive a list of all the names of the project versions that existed in the
repository. Our first problem was that Maven repository hosts projects from languages other than Java, typically languages that produce executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy, Clojure etc. These projects were filtered out by a series of filter and checks in the repository data and metadata.

In addition, we implemented a series of checks in the \textit{worker} scripts that checked if the jars are valid in terms of language implementation. After the project filtering we narrowed down our data set to 17,055 projects with 114,399 versions. Table \ref{tbl:repository} summarises the data set information and in addition provides the basic descriptive statistic measurements

We aforementioned that the Maven repository hosts software projects, typically libraries that are downloaded as dependencies with the maven tool. Each project has a series of versions.
